Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-05 contents/evaluation.tex
Updates from ShareLaTeX

@@

\subsection{Benchmark Against State-of-the-art}
\label{exp:benchmark}
This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting. We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary. Dense scale-invariant feature transform (DSIFT)\cite{PoseletsICCV09} feature is used from image representation for our model. Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset. Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton. For our model, joints are projected from the dense correspondence generated from our proposed method.

Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are reported in Table \ref{tab:hand_benchmark}. Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms. In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.

@@

\begin{table}[b!]
    \small
    \centering
    \begin{tabular}{|l|c|c|c||c|c|c|}
        \hline
                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
        \hline
        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
        \hline\hline
        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
        \hline\hline
        Ours                & \textbf{6.791}& \textbf{10.910}   & \textbf{63.1\%}       & \textbf{8.250}     &  \textbf{10.564}        & 52.1\%\\
        \hline
    \end{tabular}
    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
    \label{tab:hand_benchmark}
\end{table}

\subsection{Internal Evaluation}
\label{exp:internal}

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow_joints}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist_joints}
    \end{subfigure}
    \caption{Hand Benchmark.}
    \label{fig:internal_benchmark}
\end{figure}

\subsection{Qualitative Results}
\label{exp:qualitative}

>>>>

\begin{figure}[t!]
    \centering
    % \begin{subfigure}[b]{0.05\textwidth}
    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_1}
    \end{subfigure}
  	\hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_2}
    \end{subfigure}
    \hfill
    % \begin{subfigure}[b]{0.07\textwidth}
    %         \includegraphics[height=4.8cm]{resources/Fig_Variance/image_3}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_4}
    \end{subfigure}
  	\hfill
    % \begin{subfigure}[b]{0.05\textwidth}
    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
    % \end{subfigure}
    % \hfill
    \begin{subfigure}[b]{0.08\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_6}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.125\textwidth}
            \includegraphics[height=5.5cm]{resources/Fig_Variance/variances}
    \end{subfigure}
    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\subsection{Arm Pose Estimation}
\label{exp:benchmark}
This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting. We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary. Dense Scale-Invariant Feature Transform (SIFT)\cite{PoseletsICCV09} feature is used from image representation for our model. Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset. Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton. For our model, joints are projected from the dense correspondence generated from our proposed method.

Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are reported in Table \ref{tab:hand_benchmark}. Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms. In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation. Detailed statistical results please refer to supplementary material.

@@

% \begin{table}[b!]
%     \small
%     \centering
%     \begin{tabular}{|l|c|c|c||c|c|c|}
%         \hline
%                             & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
%         \hline
%         \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
%         \hline\hline
%         Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
%         Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
%         Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
%         Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
%         Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
%         Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
%         \hline\hline
%         Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
%         \hline
%     \end{tabular}
%     \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
%     \label{tab:hand_benchmark}
% \end{table}

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:internal}

\subsection{Annotation Correct}
\label{exp:qualitative}
